Code for Figure 1 to Figure 3

### 2021-03-16 code_for_figure1-3.Rmd
add codes for calculating posterior mean and 95% credile interval for log2(fold change) of respiration metrics

>>>>

my_respiration %>% 
  dplyr::select(fibroblast_id, respiration) %>% 
  ungroup() %>% 
  unnest(respiration) %>% 
  dplyr::filter(fibroblast_id == target_cell_line) %>% 
  spread(Cell_line, val) %>% 
  mutate(diff_in_respiration = log2(patient) - log2(NHDF)) %>% group_by(what) %>% summarize(post_mean = mean(diff_in_respiration), low_mean = quantile(diff_in_respiration, 0.025), high_mean = quantile(diff_in_respiration, 0.975))
